Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 be.tex
fixed app b

Here we derive an expression for the Bernoulli parameter, \be
\mathcal{B} \equiv \ke +\gammaf \frac{p}{\rho}+\Phi, \ee
as a function of radius $x \equiv r/\rs$.  Straightforward manipulation of the hydrodynamic equations (eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following relationship: 
\begin{align}
\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \mathcal{B} \right) = q \kew + q \Phi,
\label{eq:enCons}
\end{align}
which upon integration from the stagnation radius $r = \rs$ outwards,
\begin{align}
  r^2 \rho v(\mathcal{B} - \mathcal{B}|_{\rs})= \int_{\rs}^{r}
    r^2 \left(\frac{3}{1+\delta}\frac{G
  \Mbh}{r}+\sigma_0^2+v_w^2 + q \Phi\right) dr,
    \label{eq:enConsInt}
\end{align}
where the right hand side makes use of the definition of $\vw^{2}$ (eq.~[\ref{eq:sigmarel}]).

@@

Analysis of equation (\ref{eq:enthAnal}) results in the following interpretation of the behavior of the Bernoulli integral as a function of the heating rate.  When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow with positive kinetic energy at infinity.  However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative; this occurs first near the stagnation radius and then the region where $\mathcal{B} < 0$ grows to larger radii as $\zeta$ is reduced further.  If $\zeta$ is just less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive asymptotic kinetic energy, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical
  $\zeta_c=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$ for core ($\Gamma=0.1$)
  galaxies. If $\zeta<\zeta_c$ outflows are only possible if the ratio
  of the stagnation radius to the influence radius exceeds a minimum
  value. Plotted as a function of the ratio of the break radius to the
  influence radius ($\rb/\rsoi$) {\emph Bottom Panel:} Mininmum value
  for ratio of the stagnation radius to the break radius, $\rs/\rb$
  for core galaxies ($\Gamma=0.1$) derived by requiring the Bernoulli
  parameter of the gas to remain positive out to the break radius
  $\rb$. This is calculated numerically from
  equation~\eqref{eq:enthAnal}.}
\end{figure}

>>>>

Here we derive an expression for the Bernoulli parameter, \be
\mathcal{B} \equiv \ke +\gammaf \frac{p}{\rho}+\Phi, \ee
as a function of radius $x \equiv r/\rs$.  Straightforward manipulation of the hydrodynamic equations (eqs.~[\ref{eq:drhodt}]-[\ref{eq:dsdt}]) results in the following relationship: 
\begin{align}
\frac{1}{r^2} \frac{d}{dr} \left(r^2 \rho v \mathcal{B} \right) = q \kew + q \Phi,
\label{eq:enCons}
\end{align}
which upon integration from the stagnation radius $r = \rs$ outwards,
\begin{align}
  r^2 \rho v\mathcal{B} = \int_{\rs}^{r}
    r^2 \left(\frac{3}{1+\delta}\frac{G
  \Mbh}{r}+\sigma_0^2+v_w^2 + q \Phi\right) dr,
    \label{eq:enConsInt}
\end{align}
where the right hand side makes use of the definition of $\vw^{2}$ (eq.~[\ref{eq:sigmarel}]).

@@

Analysis of equation (\ref{eq:enthAnal}) results in the following interpretation of the behavior of the Bernoulli integral as a function of the heating rate.  When the rate of external heating is high ($\zeta \gg 1$), then $\mathcal{B} > 0$ at all radii, requiring an outflow with positive kinetic energy at infinity.  However, as $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative near the break radius for some value of $\rs$.  When $\zeta$ is moderately less than $\zeta_c$, then we can have still $\mathcal{B} > 0$ at the break radius, but only if $\rs$ exceeds a minimum value, $r_{\rm s,min}$, which increases from 0 when $\zeta = \zeta_c$ to $\sim r_{b}$ as $\zeta$ is decreased well below $\zeta_c$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value $\zeta_c$ of the wind heating parameter
  $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of the flow $\mathcal{B}$ is positive near the break radius for some value of $\rs$, calculated for core ($\Gamma=0.1$)
  galaxies using equation~\eqref{eq:enthAnal}.. {\emph Bottom Panel:} Minimum value of the stagnation radius for which $\mathcal{B} > 0$ at the break radius as a function of $\zeta/\zeta_c < 1$, again calculated for core galaxies ($\Gamma=0.1$).}
\end{figure}
